Physcraper: Body

### 2020-07-02 2-body.Rmd
kinsey comment pipelines

Many useful computational tools have been developed in an effort to make sense of the large amount of data in public molecular databases, as well as private ones. Generally referred to as "pipelines", most of these tools were motivated by the genomics revolution, to help researchers to deal with the massive amount of data, and automatically identify clusters of homologs for genomic assembly. Notably, this homolog DNA clusters can be used as homology hypotheses (i.e., molecular alignments) to reconstruct phylogenetic relationships.
Pipelines that automatize the assembly of DNA alignments from the GenBank database for phylogenetic reconstruction ("phylogenetic pipelines") such as PHYLOTA [@sanderson2008phylota], PHLAWD [@smith2009mega], and SUPERSMART [@antonelli2017toward], have been widely applied to study the evolutionary relationships among different organisms (TABLE?? maybe supplementary data), from a phylogeny of no more than 20 species of the family of barracuda fish [Sphyraenidae; @santini2013first], to a mega-phylogeny of almost 3 000 species of living ferns [Moniloformopses; @lehtonen2011towards].

Automated sequence gathering pipelines have been an important incorporation to the field of phylogenetics in many ways, particularly because they represent a clear step towards reproducibility in the field. In contrast, most published phylogenies to date have been inferred using alignments that have been assembled and curated "by hand" [@morrison2009would].
Automated approaches often suffer from errors in homology inference that could rapidly caught by human oversight. CITATION
Many systemacists support a classic phylogenetics approach (few markers thoughtfully curated) over the genomics approach (a massive amount of DNA markers that will overcome potential errors in the alignment coming from a lack of human curation).
Species tree reconstructions from multi-gene data sets taking into account the multispecies coalescent model are considered the gold standard for inferring species relationships [@song2012resolving; ROJAS ET AL. bats paper, take citations from there].
It has also been suggested that manual curation of locus alignments produces better phylogenetic reconstructions and this has been demonstrated for genomic alignments [@fragoso2017pilot].

>>>>

Computational tools are crucial to making sense of the massive amount of data in molecular databases. "Pipelines" that automate similarity based identification of DNA homologs and assembly of molecular homology hypotheses, i.e., molecular alignments [@sanderson2008phylota; @antonelli2017toward; @smith2009mega] have been a very important incorporation to the field of phylogenetics in many ways, particularly because they represent a clear step towards reproducibility in the field. They have been widely applied to study the evolutionary relationships among different organisms, from vertebrates, to plants and bacteria (TABLE OF PIPELINES AND STUDIES THAT HAVE USED THEM?? maybe supplementary data).

Still, most published phylogenies to date have been inferred using alignments that have been assembled and curated "by hand" [@morrison2009would]. GETTING AN ESTIMATE OF TOTAL PUBLISHED PHYLOGENIES WOULD BE NICE.
Automated approaches often suffer from errors in homology inference that could be rapidly caught by human oversight. CITATION
Many systemacists support a classic phylogenetics approach (few markers thoughtfully curated) over the genomics approach (a massive amount of DNA markers that will overcome potential errors in the alignment coming from a lack of human curation).
Species tree reconstructions from multi-gene data sets taking into account the multispecies coalescent model are considered the gold standard for inferring species relationships [@song2012resolving; ROJAS ET AL. bats paper, take citations from there].
It has also been suggested that manual curation of locus alignments produces better phylogenetic reconstructions and this has been demonstrated for genomic alignments [@fragoso2017pilot].

### 2020-07-02 2.1-intro-ideas.Rmd
kinsey comment pipelines

>>>>

Many useful computational tools have been developed in an effort to make sense of the large amount of data in public molecular databases, as well as private ones. Generally referred to as "pipelines", most of these tools were motivated by the genomics revolution, to help researchers to deal with the massive amount of data, and automatically identify clusters of homologs for genomic assembly. Notably, this homolog DNA clusters can be used as homology hypotheses (i.e., molecular alignments) to reconstruct phylogenetic relationships.

Pipelines that automatize the assembly of DNA alignments from the GenBank database for phylogenetic reconstruction ("phylogenetic pipelines") such as PHYLOTA [@sanderson2008phylota], PHLAWD [@smith2009mega], and SUPERSMART [@antonelli2017toward], have been widely applied to study the evolutionary relationships among different organisms (TABLE?? maybe supplementary data), from a phylogeny of no more than 20 species of the family of barracuda fish [Sphyraenidae; @santini2013first], to a mega-phylogeny of almost 3 000 species of living ferns [Moniloformopses; @lehtonen2011towards].
